---
title       : My Shiny Application
subtitle    : Example of Linear Regression
author      : jshj250
job         : Student fron Coursera
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

1. In this Shiney application, we focus on the 'mtcars' dataset.
2. You will learn to fit a linear regression model. 
$y = a + b*x$
3. The predictor (i.e. $x$) can be chosen from 'wt', 'drat' and 'qsec'.
4. The outcome (i.e. $y$) can only be 'mpg' which means the Miles/(US) gallon.
5. Use an empty line followed by three dashes to separate slides!

```{r, echo=FALSE}
data(mtcars)
summary(mtcars[,c('mpg','wt','drat','qsec')])
```

--- .class #id 

## mpg ~ wt

- You can choose 'wt' as the predictor of linear regression model.
- After you choose the predictor and the outcome, please click the following button 'Fit'. 

```{r, echo=FALSE}
fit <- lm(mpg~wt, mtcars)
par(mgp=c(2,1,0)) 
plot(fit$model[,2], fit$model[,1], xlab='Weight (lb/1000)', ylab='Miles/(US) gallon',
     main='Fit a linear regression model on the mtcars dataset')
abline(a=coef(fit)[1], b=coef(fit)[2], col='red', lwd=2)
legend("topright","fittet line",lty=1,col="red",lwd=2)
```

--- .class #id 

## mpg ~ drat
- You can choose 'drat' as the predictor of linear regression model.
- After you choose the predictor and the outcome, please click the following button 'Fit'. 

```{r, echo=FALSE}
fit <- lm(mpg~drat, mtcars)
par(mgp=c(2,1,0)) 
plot(fit$model[,2], fit$model[,1], xlab='Displacement (cu.in.)', ylab='Miles/(US) gallon',
     main='Fit a linear regression model on the mtcars dataset')
abline(a=coef(fit)[1], b=coef(fit)[2], col='red', lwd=2)
legend("topright","fittet line",lty=1,col="red",lwd=2)
```

--- .class #id 

## mpg ~ qsec
- You can choose 'qsec' as the predictor of linear regression model.
- After you choose the predictor and the outcome, please click the following button 'Fit'. 

```{r, echo=FALSE}
fit <- lm(mpg~qsec, mtcars)
par(mgp=c(2,1,0)) 
plot(fit$model[,2], fit$model[,1], xlab='1/4 mile time', ylab='Miles/(US) gallon',
     main='Fit a linear regression model on the mtcars dataset')
abline(a=coef(fit)[1], b=coef(fit)[2], col='red', lwd=2)
legend("topright","fittet line",lty=1,col="red",lwd=2)
```


